eba_sims_data

### 2020-08-23 src/eba_sims_w_data.Rmd
Add files via upload

```{r filtering_function, echo = FALSE}
# Let's build a tool to filter quickly as we please
# TODO: Let the user select multiple levels for each factor
filter_donations <- function(data, 
                             donor=NULL, donation13=NULL, site=NULL,
                             date=NULL, phleb_start=NULL, status=NULL,
                             donat_phleb=NULL, Hb=NULL, gender=NULL,
                             dob=NULL, aborh=NULL, age=NULL,
                             agegroup=NULL, Hb_deferral=NULL){
  temp <- data
  if(!is.null(donor)){
    temp <- temp[temp$donor==donor,]
  }
  if(!is.null(donation13)){
    temp <- temp[temp$donation13==donation13,]
  }
  if(!is.null(site)){
    temp <- temp[temp$site==site,]
  }
  if(!is.null(date)){
    temp <- temp[temp$date > date[1] & temp$date < date[1],]
  }
  if(!is.null(phleb_start)){
    temp <- temp[temp$phleb_start==phleb_start,]
  }
  if(!is.null(status)){
    temp <- temp[temp$status==status,]
  }
  if(!is.null(donat_phleb)){
    temp <- temp[temp$donat_phleb==donat_phleb,]
  }
  if(!is.null(Hb)){
    temp <- temp[temp$Hb > Hb[1] & temp$Hb < Hb[2],]
  }
  if(!is.null(gender)){
    temp <- temp[temp$gender==gender,]
  }
  if(!is.null(site)){
    temp <- temp[temp$site==site,]
  }
  if(!is.null(dob)){
    temp <- temp[temp$dob > dob[1] & temp$dob < dob[2],]
  }
  if(!is.null(aborh)){
    temp <- temp[temp$aborh==aborh,]
  }
  if(!is.null(age)){
    temp <- temp[temp$age > age[1] & temp$age < age[2],]
  }
  if(!is.null(agegroup)){
    temp <- temp[temp$agegroup==agegroup,]
  }
  if(!is.null(Hb_deferral)){
    temp <- temp[temp$Hb_deferral==Hb_deferral,]
  }

  return(temp)
}
```

```{r filter_test}
# Only donat_phleb="K" and status="-"
dons <- filter_donations(data = donation10, donat_phleb = "K", status = "-")

@@

```{r}
head(dons)
```

@@

```{r}
# Check
firsts[1:20,]
```

```{r}
# Attempting vectorization of the processes below

# Firsts
first_count <- as.data.frame(table(factor(firsts$date, levels=unique(firsts$date))))
# (We needed to call factor() to retain the chronological order of the rows)
colnames(first_count) <- c("week", "firsts")

@@

## Cost analysis

```{r}
actual.deferral.rate <- 76565/2464190
```

```{r}
p <- 0.031
price_ratio <- 200
surface <- cost_surface(p, price_ratio)
plot_surface(surface, price_ratio, p)
plot_interactive_surface(surface)
```

>>>>

```{r filter_test}
# Only donat_phleb="K" and status="-"
dons <- filter_donations(data = donation10, donat_phleb = "K", status = "-")
```

@@

@@

```{r}
# Firsts
first_count <- as.data.frame(table(factor(firsts$date, levels=unique(firsts$date))))
# (We needed to call factor() to retain the chronological order of the rows)
colnames(first_count) <- c("week", "firsts")

@@

```{r}
library(truncnorm)

q <- seq(0, 0.031, 0.031/1000)
x <- seq(1, 1.5, 1/10000)
adjustments <- sort(round(rtruncnorm(n=length(q), a=1, b=1.5, mean=1.1, sd=0.1), digits = 4))
E.matrix <- matrix(, nrow = 1001, ncol = 1001)
Pm <- 2
Pd <- 60 # from Satu
rl <- 0
Fn = 0.259 # Vuosikertomus 2019
qalt <- seq(0, 0.06, 0.06/1000) # Larger q
q <- seq(0, 0.031, 0.031/1000) # from data
for(i in 1:1001){
  Fratio <- adjustments[i] / (1 + Fn * (adjustments[i] - 1))
  for(j in 1:1001){
    Em <- Pm * (Fratio - 1 - q[j] * rl)
    Ed <- Pd * q[j]
    E.matrix[i, j] <- Em - Ed
    }
}

E.long <- melt(E.matrix)

```{r}
colnames(E.long) <- c("adjustment", "q", "cost")
ggplot(E.long, aes(x = q, y = adjustment, z = cost)) +
geom_tile(aes(fill=cost)) +
  stat_contour(color = "white", size = 0.7, bins = 2) +
  scale_fill_gradientn(colours=c("blue", "red")) +
labs(x="q%", y="Adjustment", title="Cost surface", subtitle = paste0("Surface minimum: ", round(min(E.long$cost), 2), ". Cost effect thresholds highlighted at 0 and -1 euros.")) +
theme_bw() +
scale_x_continuous(breaks = c(1, 1001), labels = c("0", "3.1")) +
scale_y_continuous(breaks = c(1, 1001), labels = c(as.character(min(adjustments)), as.character(max(adjustments))))
```
